---
title: "IMDb sentimental Analysis (Shyam Gandhi)"
output: word_document
---

# Extracting file from source.

```{r}
file<-read.csv("C:/Users/Shyam Gandhi/Desktop/Traintrial.csv", header = T, sep = ",")
```

# Extracting the comment text
```{r}
file_text<-file$text
```

# Convert all text to lower case 
```{r}
file_text<-tolower(file_text)
```

# Removing extra text between the words
```{r}
file_text<-gsub("\\s+", " ",file_text)
```

# For removing extra space and tab between text
```{r}
file_text<-gsub("[ |\t]{2,}"," ",file_text)
```

# For removing any space at beggining of text
```{r}
file_text<-gsub("^ ","",file_text)
```

# For removing any space at end of text
```{r}
file_text<-gsub(" $","",file_text)
```

# For removing any punctuation
```{r}
file_text<-gsub("[[:punct:]]","",file_text)
```


# For removing predifined stopwords
```{r}
library(tm)
library(stopwords)
file_text<-removeWords(file_text, stopwords("en"))
```

# For remving my own made stopwords
```{r}
file_text<-removeWords(file_text, c("film","movie","films","movies"))
```

# For removing all numbers
```{r}
file_text<-removeNumbers(file_text)
file_text<-gsub("[ |\t]{2,}"," ",file_text)
```

# For lemmatizing the string
```{r}
library(textstem)

file_text<-lemmatize_strings(file_text, language = "porter")
```

#Making corpus of text
```{r}
file_corpus<-Corpus(VectorSource(file_text))
```

# Creating term frequency matrix
```{r}
dtm<-TermDocumentMatrix(file_corpus)
m<-as.matrix(dtm)
v<-sort(rowSums(m), decreasing = T)
d<-data.frame(word=names(v), freq=v)
head(d,10)
```

#Creating WordCloud to demonstrate term frequency
```{r}
library(wordcloud)
library(RColorBrewer)

set.seed(200)
wordcloud(words = d$word, freq = d$freq, min.freq = 1, max.words = 100, random.order = F, random.color = T, colors = brewer.pal(8,"Dark2"))
```

# Ranking Sentiment
```{r}
library(syuzhet)

mysentiment<-get_nrc_sentiment(file_text)
sentiment_score<-data.frame(colSums(mysentiment[,]))
names(sentiment_score)<-"Score"
sentiment_score<-cbind("sentiment"=rownames(sentiment_score),sentiment_score)
rownames(sentiment_score)<-NULL
sentiment_score
```

#Ploting sentiment
```{r}
library(ggplot2)
ggplot(data=sentiment_score, aes(x=sentiment, y=Score))+geom_bar(aes(fill=sentiment),stat = "identity")+theme(legend.position = "none")+xlab("Sentiment")+ylab("Scores")
```

# Assigning score to each individual text
```{r}
library(sentimentr)
senti<-sentiment_by(file_text)
senti$ave_sentiment<-round(senti$ave_sentiment,3)
qplot(senti$ave_sentiment,geom = "histogram", binwidth =0.6)
sentiterms<-extract_sentiment_terms(file_text)
sentiterms$rating<-senti$ave_sentiment
head(sentiterms,10)
```



